\begin{savequote}[8cm]
  ``Learn from yesterday, live for today, hope for tomorrow. The important thing is not to stop questioning.''
  \qauthor{Albert Einstein}
\end{savequote}
\makeatletter
\chapter{Conclusion}
\label{ch:Conclusion}

In this thesis, a novel set of techniques were proposed to improve the accuracy, noise robustness, speed and storage, quantitative quality and perceptual quality of the 3D data generated when performing 3D reconstruction. To this end, several novel algorithms, data structures and techniques were proposed. First, to improve the accuracy, noise robustness, speed and qualitative and quantitative quality of 3D reconstructions, the Fourier Volume Registration algorithm and set of techniques were proposed. These techniques were tested both quantitatively using different sensor types. Findings were presented in section \ref{ch:Experiments}, the conclusions made about those results and how they tie in with the research aims are discussed in the below section (section \ref{Sec:ConcFVR}). \\

Additionally, in order to reduce storage requirements for 3D models reconstructed via a 3D reconstruction algorithm, as well as 3D models in general, a novel 3D data compression system was presented. The technique proposed, named the Plane-Tree representation, is based on Octree decomposition. Conclusions about experiments using this technique are discussed below (section \ref{Sec:ConcPT}) along with their place in the research aims and contributions for this research. \\

\section{Fourier Volume Registration}
\label{Sec:ConcFVR}

The set Fourier Volume Registration related techniques were developed as novel accurate and noise robust closed form solutions to the 3D frame registration problem within 3D reconstruction. Several techniques were proposed in this thesis. The first was the application of 3D phase correlation in registering 3D camera frames in order to align frames for reconstruction. The second was a novel 3D reconstruction / SLAM algorithm based on these 3D Fourier Phase Correlation techniques. \\

Results showed that the Fourier Volume Reconstruction method was robust to noise, and produced accurate 3D reconstructions both quantitatively and qualitatively. Results showed the FVR method was often a top performer in stereo reconstruction tests and when registering wider baselines (translations above 5cm and rotations above 10 degrees) and noisy data. \\

A novel speed improvement based on projections was also proposed (the FFVR algorithm). This was shown to improve speed up to 3 times. This novel speed up reduces the time it takes to find both the translation between a pair of frames as well as the scale and rotation separating them. Another algorithm, the MVVR method was tested on Monocular data in which depth was generated implicitly using stereo/optical flow based methods. These results showed that the MVVR method could register some of these frames in terms of translation, despite the high levels of inaccuracy in the input depth maps. It is expected that the closer the depth maps are to the ground truth, the more the performance of the MVVR method approaches that of the FVR algorithm. \\

Finally, a novel technique was proposed to allow methods based on Fourier techniques to register 3D rotation (FVR-3D). This FVR-3D method can solve for arbitrary rigid transforms which is useful for 3D reconstruction. Experiments comparing the FVR-3D techniques in terms of quantitative accuracy in comparison to current methods from the literature using both active RGB-D cameras and stereo set-ups, show that the FVR-3D algorithm is the most accurate registration method in terms of minimizing registration error.  \\

\section{Plane-Tree 3D Data Compression}
\label{Sec:ConcPT}

The Plane-Tree 3D data compression scheme was developed in order to reduce the overall storage and transmission requirements of 3D data. This method was based on Octree decomposition and this technique is shown successfully to be able to reduce the storage and transmission requirements of 3D data, such as that generated via 3D reconstruction algorithms. \\

The Plane-Tree was shown to both improve upon the Octree data representation technique as well as several state-of-the-art 3D model compression algorithms. It is also shown to improve upon the Octree in terms of specialized compression of 3D frame reconstruction data. \\

\section{Research Aims Revisited}

The primary aim of this research is to improve the accuracy, noise robustness, speed and storage, quantitative quality and perceptual quality of 3D models generated from image data. Both the FVR set of techniques as well as the Plane-Tree 3D data representation method were proposed in order to make these improvements. The research questions were: \\

1. ``Can Fourier based registration techniques improve accuracy and noise robustness in 3D reconstruction applications?'' \\

and \\

2. ``Can hierarchical techniques improve compression, storage and processing of 3D reconstruction data?'' \\


Results from chapter \ref{ch:Experiments} show that the FVR based methods are accurate, robust to noise and produces qualitatively pleasant 3D reconstructions. Quantitative tests reveal that the FVR method improves upon existing solutions in terms of both accuracy and noise robustness on wider baselines. Results also show the FVR-3D algorithm outperforms others from the literature when registering data from active sensors or stereo camera pairs. Therefore the answer to question 1. is yes, Fourier based registration techniques can improve accuracy and noise robustness in 3D reconstruction applications. \\


Results also reveal that hierarchical technique, the Plane-Tree improves upon existing storage and compression solutions for both 3D data and specifically for 3D data produced by 3D reconstruction algorithms. Therefore the answer to the second research question is yes, hierarchical techniques can improve compression, storage and processing of 3D reconstruction data. \\

\section{Future Work}

There is still much work to be done in the both the area of Fourier 3D reconstruction techniques as well hierarchical data storage, processing and transmission. Further development of the FVR technique is required as presently it relies on the fact that no frame to frame registrations fail. That is there should be some filtering of registration data via Kalman filter or something similar in order to reduce the error in case an accurate registration cannot be produced. Secondly, there are still many octant representation methods to test and develop within the field of Hierarchical data compression. Further research could also be performed in terms of integrating each frame efficiently into the structure as it is registered. \\
